---
title: "R Week 1 Demonstrations"
author: "Bonhwang Koo & Jon Clucas"
date: "2017 January 5"
output: html_notebook
---

Getting Started

Commands: evaluated by R interpreter

help(function)
```{r}
help(help)
```

or ?function
```{r}
?c
```

example(function)
```{r}
example(c)
```

Vectors and Variables
```{r}
x <- 7
y <- "diagnosis"
3.42 -> z
a <- z
b <- y -> c
```

The escape character `\`
```{r}
?Quotes
```

Environments, Sessions, and Workspaces
```{r}
?rm
rm(a)
```

Data Types & Structures
```{r}
my_char <- "Hello"
typeof(my_char)

my_num <- 1.4
typeof(my_num)

my_logical <- TRUE
typeof(my_logical)
```

```{r}
empty_vector_1 <- vector()
empty_vector_1

empty_vector_2 <- vector("character", length = 12)
empty_vector_2
typeof(empty_vector_2[0])
```

```{r}
character(5)
numeric(5)
logical(5)
```

```{r}
nums <- c(1,2,3)
nums

length(nums)

nums[2] = 10
nums
```

```{r}
nums2 <- 1:100
nums2
```

```{r}
nums3 <- seq(40)
nums3

nums4 <- seq(1, 10, by = .2)

#Can also add to a vector
nums5 <- c(nums4, 101)
nums5
```

When you mix types in a vector, R coerces all the elements to one type
```{r}
va <- c("char", 1, 1.0)
vb <- c(TRUE, 1, 97)
vc <- c(TRUE, 1, 0)
vd <- c("What", TRUE, FALSE)

typeof(va[2])
typeof(vb[1])
typeof(vc[1])
typeof(vd[2])
```

Matrices
```{r}
m <- matrix(nrow = 3, ncol = 4)
dim(m)
m
```

```{r}
m[1,1] = TRUE
m
m[1,2] = FALSE
m
```

Can reference an entire row or column of a matrix
```{r}
m[2,] = TRUE
m
```

```{r}
m1 <- matrix(1:10, nrow = 5, ncol = 2)
m1
```

```{r}
m2 <- 1:25
dim(m2) <- c(5,5)
m2
```

```{r}
m3 <- rbind(c(1:3), c(4:6), c(7:9))
m3
```

```{r}
m4 <- cbind(c(100:149), c(150:199), c(200:249))
m4
```

Lists
```{r}
l <- list(1, TRUE, "three")
list_w_in_list <- list(FALSE, 2, l)
list_w_in_list[[4]] <- "This is the 4th item in the list"
list_w_in_list[[4]][[2]] <- "This is the 2nd part of the 4th item in the list"
list_w_in_list
```

Data Frames
```{r}
df <- data.frame(id = c(1:10), isOdd = c("Yes", "No", "Yes", "No", "Yes", "No", "Yes", "No", "Yes", "No"), 
                 isEven = c(FALSE, TRUE, FALSE, TRUE, FALSE, TRUE, FALSE, TRUE, FALSE, TRUE))
```

```{r}
head(df)
```

```{r}
tail(df)
```

```{r}
dim(df)
```

```{r}
nrow(df)
```

```{r}
ncol(df)
```

```{r}
str(df)
```

```{r}
names(df)
```

```{r}
df$isEven
```

```{r}
df[2,1]
```

```{r}
df[4,]
```

Factors
```{r}
odd = factor(df$isOdd)
odd
```

Operators
```{r}
x + z
x - z
x * z
x / z
x ^ z
x %% z
x %/% z
```

```{r}
x < z
x > z
x == z
x >= z
x <= z
```

numerator/denominator = integer quotient remainder / denominator
```{r}
quotient = 10 / 3
quotient
```

```{r}
integer_quotient = 10 %/% 3
modulus = 10 %% 3
integer_quotient
modulus
```

```{r}
quotient == integer_quotient + modulus / 3
```

```{r}
sqrt(x)
exp(x) # e^x
log(x)
-log(exp(x))
abs(-log(exp(x)))
```

```{r}
3 + 4
exp(1)
log(100)
abs(-100)
```

```{r}
x <- 100 - 2
y <- 1.0 * 2
z <- 10 / 3.0
a <- 10%%2
b <- 10%%3
c <- 10%/%2
d <- 10%/%3
e <- sqrt(25)
```

```{r}
x
y
z
a
b
c
d
e
```

Strings
```{r}
my_string <- "/Users/Username/Desktop/filename.csv"
```

```{r}
nchar(my_string)
```

```{r}
print(my_string)
print("hello world!")
```

```{r}
this_string <- "HeLlO WoRlD"
tolower(this_string) #Note: this_string itself does not actually change
toupper(this_string)
this_string
```

Substrings and concatenation
```{r}
new_string1 = substring(this_string, 1, 3)
new_string2 = substring(this_string, 4) #if there is no 3rd argument, R defaults to the very end of the string
paste(new_string1, new_string2)
```

```{r}
paste("This", "Sentence", "Is", "Separated", "by", "Forward", "Slashes", sep = "/")
```
