---
title: "R_Week_3_Exercises"
author: "Jon Clucas and Bonhwang Koo"
output: html_document
---

Set the working directory and read in some data.
```{r}
path <- "/Volumes/Data/Research/CDB/RA Didactics/Programming_Jan2017/Week 3/example_csv/"
setwd(path)

plot1_data <- read.csv("MFCCs_close_off.csv")
```

Build a scatterplot.
```{r}
plot(plot1_data$amean, plot1_data$max)
```
•••••
Draw a line of best fit on your scatterplot.
```{r}
plot(plot1_data$amean, plot1_data$max)
abline(lm(plot1_data$max ~ plot1_data$amean))
summary(lm(plot1_data$max ~ plot1_data$amean))
```
•••••
Connect the dots on your scatterplot.
```{r}
plot()
lines()
```
•••••
Create a data frame from the SM KBIT Data
```{r}
sm_kbit_data <- read.csv("/Volumes/Data/Research/CDB/RA Didactics/Programming_Jan2017/Week 3/example_csv/SM_EEG_KBIT.csv")
```
Create a boxplot comparing KBIT IQ scores between SM and control groups
```{r}
boxplot(sm_kbit_data$KBIT.IQ.Standard.Score ~ sm_kbit_data$SM_dx)
```
•••••
Conduct a t-test comparing KBIT IQ scores for SM and control participants
```{r}
t.test(sm_kbit_data$KBIT.IQ.Standard.Score ~ sm_kbit_data$SM_dx)
```
•••••

•••••
Plot 2 or more datasets in a single scatterplot
```{r}

```

Look at a summary of the linear model for each dataset in your scatterplot
```{r}

```

Plot Screen vs min MFCC values in m2
```{r}
path <- "/Volumes/Data/Research/CDB/RA Didactics/Programming_Jan2017/Week 3/example_csv/"
setwd(path)
mfccs <- read.csv("openSMILE_emobase_MFCCs.csv")
m2 <- cast(data=mfccs, formula = Distance + Screen + Coefficient ~ Functional)

plot({coefficeint vector}, {minimum value vector}) # first Screen factor
abline()

points() # second Screen factor
abline()
```

Choose a functional from m2 (any of the columns after "Coefficient"). Plot an interaction.plot with Distance & Screen against that functional.
```{r}

```

Use summary(aov()) to compare the functional you interaction.plotted to Distance and Screen.
```{r}

```


Use aov() to compare SM KBIT_Verbal to KBIT_Nonverbal
```{r}
path <- "/Volumes/Data/Research/CDB/RA Didactics/Programming_Jan2017/Week 3/example_csv/"
setwd(path)
sm_kbit = read.csv("/Volumes/data/Research/CDB/RA Didactics/Programming_Jan2017/Week 3/example_csv/SM_EEG_KBIT.csv")

```

