---
title: "R Week 5 Demonstrations & Exercises"
author: "Bonhwang Koo & Jon Clucas"
date: "2017 February 8"
output: html_notebook
---
Install necessary libraries
```{r}
install.packages("sqldf") # for sqldf() function to organize data into long form
install.packages("tidyr") # for gather() function
install.packages("plotrix") # for error bars
```

Load necessary packages
```{r}
library("sqldf")
library("tidyr")
library("plotrix")
library("dplyr")
```

Get & format data for ANOVA
```{r}
sm_raw_n42 <- read.csv("/Volumes/Data/Research/CDB/RA\ Didactics/Programming_Jan2017/Week\ 5/sample_data/n42.csv")
names(sm_raw_n42)[names(sm_raw_n42)=="ursi"] <- "Subject_ID"
sm_raw_n37 = subset(sm_raw_n42, reverse == 0)

##RT DATA: Create RT dataframe, long version

RT_raw_n37 <- sqldf ('select Subject_ID, sm_dx,
                     rt_button_press_no_exp, rt_button_press_w_exp, 
                     rt_vocal_no_exp, rt_vocal_w_exp
                     from sm_raw_n37')

#remove m00446668, m00456481, and m00474331
RT_raw_n34 = na.omit(RT_raw_n37)

RT_data_long_n34 <- gather(RT_raw_n34, condition, RT, rt_button_press_no_exp:rt_vocal_w_exp)

RT_Data_n34 <- sqldf ('select Subject_ID, sm_dx, RT,
                      case
                      when Condition = "rt_button_press_no_exp" then 1
                      when Condition = "rt_button_press_w_exp" then 1
                      else 0
                      end as Response_Mode,
                      case
                      when Condition = "rt_button_press_w_exp" then 1
                      when Condition = "rt_vocal_w_exp" then 1
                      else 0
                      end as Stranger
                      from RT_data_long_n34
                      order by "Subject_ID"')

##VOLUME DATA: Create Volume dataframe, long version

Volume_raw_n37 <- sqldf ('select Subject_ID, sm_dx,
                         ampl_vocal_no_exp, ampl_vocal_w_exp
                         from sm_raw_n37')

#remove m00446668 and m00474331
Volume_raw_n35 = na.omit(Volume_raw_n37)

Volume_Data_Long_n35 <- gather(Volume_raw_n35, condition, Volume, ampl_vocal_no_exp:ampl_vocal_w_exp)

Volume_Data_n35 <- sqldf ('select Subject_ID, sm_dx, Volume, 
                          case
                          when Condition = "ampl_vocal_w_exp" then 1
                          else 0
                          end as Stranger
                          from Volume_Data_Long_n35
                          order by "Subject_ID"')

##ACCURACY DATA: Create accuracy dataframe, long version
#I am renaming "Performance" as "Accuracy" for clarity.
#NOTE: make sure accuracy is presented as a percentage (because it's the # trials correct out of 50).

#need to recalculate acc as percentage.

Perf_raw_n37 <- sqldf ('select Subject_ID, sm_dx,
                       perf_button_press_no_exp, perf_button_press_w_exp, 
                       perf_vocal_no_exp, perf_vocal_w_exp
                       from sm_raw_n37')

Perf_data_long_n37 <- gather(Perf_raw_n37, condition, Accuracy, perf_button_press_no_exp:perf_vocal_w_exp)

Acc_Data_n37 <- sqldf ('select Subject_ID, sm_dx, Accuracy,
                       case
                       when Condition = "perf_button_press_no_exp" then 1
                       when Condition = "perf_button_press_w_exp" then 1
                       else 0
                       end as Response_Mode,
                       case
                       when Condition = "perf_button_press_w_exp" then 1
                       when Condition = "perf_vocal_w_exp" then 1
                       else 0
                       end as Stranger
                       from Perf_data_long_n37
                       order by "Subject_ID"')
```

Repeated measures ANOVA with one IV
```{r}
#Volume ANOVA with one group
fit_Volume_n35_no_dx <- aov(Volume~Stranger+Error(Subject_ID/(Stranger)),
                      data=Volume_Data_n35)
summary(fit_Volume_n35_no_dx)
#Volume ANOVA with two groups
fit_Volume_n35 <- aov(Volume~(Stranger*sm_dx)+Error(Subject_ID/(Stranger))+(sm_dx),
                      data=Volume_Data_n35)
summary(fit_Volume_n35)
```
Visualize Volume ANOVA
```{r}
library(ggplot2)
ggplot(Volume_Data_n35, aes(x=factor(Stranger), y=Volume, fill=factor(sm_dx))) + geom_boxplot()
```

Repeated measures ANOVA with two IVs
```{r}
#Acc ANOVA
fit_Acc_n37 <- aov(Accuracy~(Response_Mode*Stranger*sm_dx)+Error(Subject_ID/
                  (Response_Mode*Stranger))+(sm_dx), data=Acc_Data_n37)
summary(fit_Acc_n37)
```

Visualize Acc ANOVA
```{r}
ggplot(Acc_Data_n37, aes(x=factor(sm_dx, labels = c("control", "SM")), y=Accuracy, col=factor(Stranger, labels= c("no", "yes")))) + stat_summary(fun.y=mean, geom = "point") + stat_summary(fun.y=mean, geom = "line", aes(group = factor(Stranger))) + guides(col=guide_legend(title="Stranger")) + labs(x = "SM dx", title = "Accuracy by stranger presence & SM diagnosis") + expand_limits(y=c(65,100))
```

Try repeated measures ANOVA with two IVs for 
```{r}
#RT ANOVA
fit_RT_n34 <- 
summary(fit_RT_n34)
```

Visualize RT ANOVA
```{r}

```

Biclustering
Install libraries for biclustering
```{r}
install.packages("viridis")
install.packages("gplots")
```

Load libraries for biclustering
```{r}
library(viridis)
library(gplots)
```

Get data for biclustering
```{r}
setwd("/Volumes/data/Research/CDB/RA Didactics/Programming_Jan2017/Week 5/sample_data")
##Import Data
Quotient_All <- read.csv("BiCluster2.csv")
Quotient_All <- na.omit(Quotient_All)
ADHD_Dx <- read.csv("ADHD_1.csv")
```

Reformat data for biclustering
```{r}
#Select Subgroup for clustering
Q_Older <- Quotient_All[which(Quotient_All$Age>=11.000),]
##Separate demos
Q_Older_Demos<-Q_Older[1:3]
##Remove demos from data for clustering
Q_Older<-Q_Older[,c(1,4:27)]
#Separate ID column
rnames3 <- Q_Older[,1]
Q_Older2 <- data.matrix(Q_Older[, c(2:25)])
rownames(Q_Older2) <- rnames3

##Center and scale the data
Qscale3 <- scale(Q_Older2)
```

Cluster the rows
```{r}
hr <- hclust(as.dist(1-cor(t(Qscale3), method="spearman")), method="ward.D2")
```

Cluster the columns
```{r}
hc <- hclust(as.dist(1-cor(Qscale3, method="spearman")), method="ward.D2")
```

Create cut tree for rows
```{r}
mycl2 <- cutree(hc, h=max(hr$height)/5.0); mycolhr <- rainbow(length(unique(mycl2)), start=0.1, end=0.9); 
mycolhr <- mycolhr[as.vector(mycl2)]
```

Create cut tree for columns
```{r}
mycl <- cutree(hr, h=max(hr$height)/1.5); mycolhc <- rainbow(length(unique(mycl)), start=0.1, end=0.9);
mycolhc <- mycolhc[as.vector(mycl)]
```

Create a heatmap
```{r}
heatmap.2(Qscale3,
          Rowv=as.dendrogram(hr),
          Colv=as.dendrogram(hc),
          col="viridis",
          scale="row",
          density.info="none",
          trace="none",
          margins = c(9, 2),
          srtRow = 0,
          srtCol = 60,
          keysize = 1,
          key.title = NA,
          main = NULL,
          RowSideColors=mycolhc,
          ColSideColors = mycolhr)
```

