---
title: "R_Week2_Exercises"
author: "Jon Clucas and Bonhwang Koo"
output: html_document
---

Download your choice of .csv files from Google Drive (Week 2)
Move the .csv files to a folder on your computer or drive (not the CMI server)
Set the working directory to this folder
Create a vector containing the file names in your folder
Run a loop to print out all the file names, including the path, in the folder
Create a data frame variable from a csv of your choice
```{r}
path <- "/Users/jon.clucas/Downloads/example_csv"
setwd(path)
file_names <- list.files(path=path, pattern="*.csv")

for (i in 1:length(file_names)) { # Change the parenthetical statement to iterate through the vector file_names, from 1 to the vector length
  print(file.path(path, file_names[i]))
}

df <- read.csv(file.path(path, file_names[8]))

```

Create a vector that contains boolean values comparing the 2 strings in each row of the dataframe
Determine if all the values of the new vector are TRUE
```{r}
isEqual <- df$X2017.01.03_ArnoR_Rode__Canon_.Watson..json == df$X2017.01.03_ArnoR_Sony_.Watson..json

all(isEqual)
```

For each of the two columns, create a vector that contains the length of each string
Sort each vector by decreasing order
Print summary statistics for each vector
Compare mean and variance for each vector
```{r}
lengths1 <- nchar(levels(df$X2017.01.03_ArnoR_Rode__Canon_.Watson..json))
lengths2 <- nchar(levels(df$X2017.01.03_ArnoR_Sony_.Watson..json))

lengths1 <- sort(lengths1, decreasing = TRUE)
lengths2 <- sort(lengths2, decreasing = TRUE)

summary(lengths1)
summary(lengths2)

mean1 <- mean(lengths1)
mean2 <- mean(lengths2)
var1 <- var(lengths1)
var2 <- var(lengths2)

mean1 == mean2
var1 == var2
```

For lengths1, create a new vector that only contains strings that are longer than the mean length
Repeat for lengths2

Double the value of each element in each new vector
```{r}
greaterThanAvg1 <- levels(df$X2017.01.03_ArnoR_Rode__Canon_.Watson..json)[lengths1 > mean1]
greaterThanAvg2 <- levels(df$X2017.01.03_ArnoR_Sony_.Watson..json)[lengths2 > mean2]

lengths1 <- lengths1[lengths1 > mean1] * 2
lengths2 <- lengths2[lengths2 > mean2] * 2
```

Using a loop of your choice, replace the values in lengths1 with a random number 
  (try using rnorm(1), which generates a random number from a normal distribution)
```{r}
for(i in 1:length(lengths1)){
  lengths1[i] <- round((1 + lengths1[i] + lengths1[i] * rnorm(1)), 0)
}
lengths1
```

