---
title: "R_Week2_Exercises"
author: "Jon Clucas and Bonhwang Koo"
output: html_document
---

Download your choice of .csv files from Google Drive (Week 2)
Move the .csv files to a folder on your computer or drive (not the CMI server)
Set the working directory to this folder
Create a vector containing the file names in your folder
Run a loop to print out all the file names, including the path, in the folder
Create a data frame variable from a csv of your choice
```{r}
path <- "Path to working directory"
setwd(path)
file_names <- NULL

for (i in 1:1) { # Change the parenthetical statement to iterate through the vector file_names, from 1 to the vector length
  print("Your code here")
}

df <- read.csv("filename")

```

Create a vector that contains boolean values comparing the 2 strings in each row of the dataframe
Determine if all the values of the new vector are TRUE
```{r}
isEqual = "" == ""

```

For each of the two columns, create a vector that contains the length of each string
Sort each vector by decreasing order
Print summary statistics for each vector
Compare mean and variance for each vector
```{r}
lengths1 = NA
lengths2 = NA

mean1 = 0
mean2 = 0
var1 = 0
var2 = 0
```

For lengths1, create a new vector that only contains strings that are longer than the mean length
Repeat for lengths2

Double the value of each element in each new vector
```{r}
greaterThanAvg1 = lengths1[]
greaterThanAvg2 = lengths2[]


```

Using a loop of your choice, replace the values in lengths1 with a random number 
  (try using rnorm(1), which generates a random number from a normal distribution)
```{r}

```

