---
title: "R Week 3 Demonstrations"
author: "Bonhwang Koo & Jon Clucas"
date: "2017 January 26"
output: html_notebook
---

Set the working directory and read in some data
```{r}
path <- "/Volumes/Data/Research/CDB/RA Didactics/Programming_Jan2017/Week 3/example_csv/"
setwd(path)

close_on <- read.csv("MFCCs_close_on.csv")
```

Plot the maximum value for each coefficient.
```{r}
plot(close_on$max)
```

Plot the time of the maximum value (x-axis) vs the maximum value (y-axis) for each coefficient.
```{r}
plot(close_on$maxPos, close_on$max)
```

Give the plots and axes labels.
```{r}
plot(close_on$max, main="MFCC maximum values: microphone close, pop screen on", xlab = "coefficient", ylab = "maximum value")
plot(close_on$maxPos, close_on$max, main = "MFCC maximum value: microphone close, pop screen on", xlab = "position of maximum value (frames)", ylab = "maximum value")
```

Play with graphical parameters.
```{r}
plot(close_on$max, main="MFCC maximum values: microphone close, pop screen on", xlab = "coefficient", ylab = "maximum value", xlim=c(-12, 12), ylim=c(0-max(close_on$max), max(close_on$max)), pch=13)
```

Change the points on the first plot to time labels.
```{r}
plot(close_on$max, main="MFCC maximum values: microphone close, pop screen on", xlab = "coefficient", ylab = "maximum value", type="n")
text(close_on$max, labels=close_on$maxPos)
```

Change the points on the second plot to coefficient labels.
```{r}
plot(close_on$maxPos, close_on$max, main = "MFCC maximum value: microphone close, pop screen on", xlab = "position of maximum value (frames)", ylab = "maximum value", type="n")
text(close_on$maxPos, close_on$max, labels=close_on$Coefficient)
```
•••••
Draw a line x = y on a simple plot.
```{r}
plot(c(1, 3, 2))
abline(0, 1)
```

Draw a line of best fit on the first plot.
```{r}
plot(close_on$max, main="MFCC maximum values: microphone close, pop screen on", xlab = "coefficient", ylab = "maximum value", pch=13)
abline(lm(close_on$max ~ close_on$Coefficient))
```

Draw a line of best fit on the second plot.
```{r}
plot(close_on$maxPos, close_on$max, main = "MFCC maximum value: microphone close, pop screen on", xlab = "position of maximum value (frames)", ylab = "maximum value", type="n")
text(close_on$maxPos, close_on$max, labels=close_on$Coefficient)
abline(lm(close_on$max ~ close_on$maxPos))
```

Look at the linear model fitting the plots.
```{r}
lm(close_on$max ~ close_on$Coefficient)
lm(close_on$max ~ close_on$maxPos)
```
•••••
Get a second dataset to add a second graph to the second plot.
```{r}
path <- "/Volumes/Data/Research/CDB/RA Didactics/Programming_Jan2017/Week 3/example_csv/"
setwd(path)

far_off <- read.csv("MFCCs_far_off.csv")
```

Add a second graph to the second plot.
```{r}
plot(close_on$maxPos, close_on$max, main = "MFCC maximum value", sub="close & screen on vs far & screen off", xlab = "position of maximum value (frames)", ylab = "maximum value", type="n", xlim=c(min(c(close_on$maxPos, far_off$maxPos)), c(max(c(close_on$maxPos, far_off$maxPos)))), ylim=c(min(c(close_on$max, far_off$max)), c(max(c(close_on$max, far_off$max)))))
text(close_on$maxPos, close_on$max, labels=close_on$Coefficient)
abline(lm(close_on$max ~ close_on$maxPos))

points(far_off$maxPos, far_off$max, type="n")
text(far_off$maxPos, far_off$max, labels=far_off$Coefficient, col="blue")
abline(lm(far_off$max ~ far_off$maxPos), col = "blue")
```

Put a legend on that last plot.
```{r}
plot(close_on$maxPos, close_on$max, main = "MFCC maximum value", xlab = "position of maximum value (frames)", ylab = "maximum value", type="n", xlim=c(min(c(close_on$maxPos, far_off$maxPos)), c(max(c(close_on$maxPos, far_off$maxPos)))), ylim=c(min(c(close_on$max, far_off$max)), c(max(c(close_on$max, far_off$max)))))
text(close_on$maxPos, close_on$max, labels=close_on$Coefficient)
abline(lm(close_on$max ~ close_on$maxPos))
points(far_off$maxPos, far_off$max, type="n")
text(far_off$maxPos, far_off$max, labels=far_off$Coefficient, col="blue")
abline(lm(far_off$max ~ far_off$maxPos), col = "blue")
legend(320, 42, c("close & screen on", "far & screen off"), pch = c(13, 23), col = c("black", "blue"), text.col = c("black", "blue"))
```

Draw the second plot with the points connected.
```{r}
plot(close_on$maxPos, close_on$max, main = "MFCC maximum value: microphone close, pop screen on", xlab = "position of maximum value (frames)", ylab = "maximum value", type="n")
text(close_on$maxPos, close_on$max, labels=close_on$Coefficient)
lines(close_on$maxPos, close_on$max)
```

Get the hamming data and make a dotchart.
```{r}
hamming <- read.csv("/Volumes/Data/Research/CDB/RA Didactics/Programming_Jan2017/Week 3/example_csv/hamming.csv")
dotchart(hamming$Hamming.Distance, labels = hamming$Screen, groups=hamming$Distance, lcolor="purple", main="Microphone Placement", sub="grouped by physical distance", xlab="Hamming Distance", ylab="Pop Screen", xlim=c(0,max(hamming$Hamming.Distance)), pch=4, color="purple")
```
•••••
mtcars is a built-in dataframe
```{r}
attach(mtcars) # Sample dataset for cars
head(mtcars) # Show the first 6 rows of mtcars
```

Scatter plot for MPG vs. Weight (tons) with some modifications
```{r}
plot(mtcars$wt, mtcars$mpg, main = "Auto Fuel Efficiency vs. Weight",
     xlab = "Weight (tons)", ylab = "Fuel Efficieny (Miles per Gallon)",
     xlim = c(0, 6), ylim = c(0, 40), pch = 21)
abline(lm(mtcars$mpg ~ mtcars$wt), col = "blue")
```

Look at the summary of the linear model with intercept and slope for line of best fit
```{r}
mtcars_lm <- lm(mtcars$mpg ~ mtcars$wt)
summary(mtcars_lm)
```

Create a dataframe from SM KBIT data & abbreviate column names
```{r}
sm_kbit = read.csv("/Volumes/data/Research/CDB/RA Didactics/Programming_Jan2017/Week 3/example_csv/SM_EEG_KBIT.csv")

names(sm_kbit)[names(sm_kbit) == "KBIT.Verbal.Standard.Score"] = "KBIT_Verbal"
names(sm_kbit)[names(sm_kbit) == "KBIT.Nonverbal.Standard.Score"] = "KBIT_Nonverbal"
names(sm_kbit)[names(sm_kbit) == "KBIT.IQ.Standard.Score"] = "KBIT_IQ"
```

T-test comparing Verbal scores between SM and controls
```{r}
t.test(sm_kbit$KBIT_Verbal ~ sm_kbit$SM_dx)
```

T-test comparing Verbal and Nonverbal scores between all participants
```{r}
t.test(sm_kbit$KBIT_Verbal, sm_kbit$KBIT_Nonverbal, paired = TRUE) # Note: If the argument "paired" is not specified, it defaults to FALSE
```

Boxplot comparing Verbal scores between SM and controls
```{r}
boxplot(KBIT_Verbal ~ SM_dx, data = sm_kbit)
```

Boxplot with modifications
```{r}
png(filename = "/Volumes/Data/Research/CDB/RA Didactics/Programming_Jan2017/Week 3/KBIT_boxplot_modified.png") # Specify where to save image as .png
boxplot(KBIT_Verbal ~ SM_dx, data = sm_kbit, main = "KBIT Verbal Scores", 
        xlab = "SM Diagnosis", ylab = "KBIT Verbal Score",
        ylim = c(50, 150), col = c("#0067A0", "#919d9d"))
dev.off()
```

Get complete microphone placement data for ANOVA
```{r}
library("reshape") # if R can't find function cast
setwd(path)
mfccs <- read.csv("openSMILE_emobase_MFCCs.csv")
m2 <- cast(data=mfccs, formula = Distance + Screen + Coefficient ~ Functional)
```

ANOVA: Distance vs max MFCC values
```{r}
distance_to_max <- aov(max ~ Distance, data=m2)
summary(distance_to_max)
```

Plot Distance vs max MFCC values
```{r}
plot(m2[m2$Distance == "close", ]$Coefficient, m2[m2$Distance == "close", ]$max, pch=19, ylab = "max MFCC value", xlab="MFCC coefficient")
abline(lm(m2[m2$Distance == "close", ]$max ~ m2[m2$Distance == "close", ]$Coefficient), col="black")
points(m2[m2$Distance == "far", ]$Coefficient, m2[m2$Distance == "far", ]$max, pch=20, col="grey")
abline(lm(m2[m2$Distance == "far", ]$max ~ m2[m2$Distance == "far", ]$Coefficient), col="grey")
legend(0.5, 42, c("close", "far"), pch = c(19, 20), col = c("black", "grey"), text.col = c("black", "grey"), title="Mic Distance")
```

Plot aov
```{r}
plot(distance_to_max)
```

ANOVA: Distance & Screen vs min MFCC values
```{r}
ds_to_min <- aov(max ~ Distance*Screen, data=m2)
summary(ds_to_min)
```

Plot Distance & Screen vs min MFCC values
```{r}
plot(m2[m2$Distance == "close" & m2$Screen == "on", ]$Coefficient, m2[m2$Distance == "close" & m2$Screen == "on", ]$min, pch=19, ylab = "min MFCC value", xlab="MFCC coefficient")
abline(lm(m2[m2$Distance == "close" & m2$Screen == "on", ]$min ~ m2[m2$Distance == "close" & m2$Screen == "on", ]$Coefficient), col="black")

points(m2[m2$Distance == "close" & m2$Screen == "off", ]$Coefficient, m2[m2$Distance == "close" & m2$Screen == "off", ]$min, pch=21, col="green")
abline(lm(m2[m2$Distance == "close" & m2$Screen == "off", ]$min ~ m2[m2$Distance == "close" & m2$Screen == "off", ]$Coefficient), col="green")

points(m2[m2$Distance == "far" & m2$Screen == "on", ]$Coefficient, m2[m2$Distance == "far" & m2$Screen == "off", ]$min, pch=20, col="grey")
abline(lm(m2[m2$Distance == "far" & m2$Screen == "on", ]$min ~ m2[m2$Distance == "far" & m2$Screen == "on", ]$Coefficient), col="grey")

points(m2[m2$Distance == "far" & m2$Screen == "on", ]$Coefficient, m2[m2$Distance == "far" & m2$Screen == "off", ]$min, pch=1, col="blue")
abline(lm(m2[m2$Distance == "far" & m2$Screen == "off", ]$min ~ m2[m2$Distance == "far" & m2$Screen == "off", ]$Coefficient), col="blue")

legend(0.5, -42, c("close & on", "close & off", "far & on", "far & off"), pch = c(19, 21, 20, 1), col = c("black", "green", "grey", "blue"), text.col = c("black", "green", "grey", "blue"), title="Mic Distance & Pop Screen")
```

plot aov
```{r}
plot(ds_to_min)
```

interaction plot for Distance & Screen vs min MFCC values
```{r}
interaction.plot(m2$Distance, m2$Screen, m2$min, ylab = "min MFCC value", xlab = "mic distance", trace.label = "pop screen")
```

