---
title: "R Week 2 Demonstrations"
author: "Bonhwang Koo & Jon Clucas"
date: "2017 January 12"
output: html_notebook
---

File Manipulation

Commands: evaluated by R interpreter

getwd()
```{r}
getwd()
```

setwd()
RStudio will reset the working directory to the default in each new block, so if you need to access the directory in a later block, you'll need to run setwd again.
Also, notice the space character is entered as `\ ` rather than just ` ` because it is a special character.
```{r}
setwd("/Volumes/Data/Research/CDB/RA\ Didactics/Programming_Jan2017/Week\ 2/example_csv")
getwd()
```

read.csv
```{r}
setwd("/Volumes/Data/Research/CDB/RA\ Didactics/Programming_Jan2017/Week\ 2/example_csv")
words_3 <- read.csv(file = "words_3.csv")
```

rename columns we want to keep
add a column to tell if the values in the original two columns are equal
remove column we don't need
write updated database to new csv file
```{r}
setwd("/Volumes/Data/Research/CDB/RA\ Didactics/Programming_Jan2017/Week\ 2/example_csv")

# rename columns we want to keep
names(words_3)[2] <- "Rode_Canon"
names(words_3)[names(words_3) == "X2017.01.03_ArnoT_Sony_.Watson..json"] <- "Sony"

# add a column to tell if the values in the original two columns are equal
words_3$col_is_equal <- (words_3$Rode_Canon == words_3$Sony)

# remove column we don't need
words_3[1] <- NULL

# write updated database to new csv file
write.csv(words_3, file = "output/words_3_edited.csv")
```

file.path
notice the opening slash to set an absolute path
```{r}
wd <- file.path("/", "Volumes", "Data", "Research", "CDB", "RA\ Didactics", "Programming_Jan2017", "Week\ 2", "example_csv")
```

list.files
```{r}
setwd(wd)
file_list <- list.files(wd)
file_list
```

$
```{r}
words_3$Sony
```

numeric vector
```{r}
fib <- c(1, 1, 2, 3, 5, 8, 13, 21, 34, 55, 89)
```

descriptive operations
```{r}
paste("mean:", mean(fib))
paste("median:", median(fib))
print("quantile:", quote = FALSE)
quantile(fib) # Divides a vector into quantiles (i.e. 0th, 25th, 50th/median, 75th, and 100th percentiles)
paste("min:", min(fib))
paste("max:", max(fib))
paste("var:", var(fib)) # variance
print("sort:", quote = FALSE)
sort(fib, decreasing = TRUE)
print("summary:", quote = FALSE)
summary(fib)
```

NA
(na.rm is TRUE by default)
```{r}
fib <- c(fib, NA)
paste("mean (na.rm = TRUE):", mean(fib, na.rm = TRUE))
paste("mean (na.rm = FALSE):", mean(fib, na.rm = FALSE))
```

Vector math
```{r}
fib <- fib[1:11]
fib_head_reversed <- sort(fib, decreasing = TRUE)

fib + fib_head_reversed

fib * 4
```

Boolean logic
```{r}
a <- TRUE
b <- !a
paste("a:", a)
paste("b:", b)

a_AND_b <- a & b
paste("a & b:", a_AND_b)
paste("a & a:", (a & a))
paste("b & b:", (b & b))

a_OR_b <- a | b
paste("a | b:", a_OR_b)
paste("a | a:", (a | a))
paste("b | b:", (b | b))

a_XOR_b <- xor(a, b)
paste("a XOR b:", a_XOR_b)
paste("a XOR a:", xor(a, a))
paste("b XOR b:", xor(b, b))
```

comparison operators
```{r}
fib[1]
fib_head_reversed[1]
"1 == 89?"
fib[1] == fib_head_reversed[1] # 1 == 89?
"1 < 89?"
fib[1] < fib_head_reversed[1]
"1 > 89?"
fib[1] > fib_head_reversed[1]
"1 <= 89?"
fib[1] <= fib_head_reversed[1]
"1 >= 89?"
fib[1] >= fib_head_reversed[1]

"1 == 1?"
fib[1] == fib_head_reversed[11] # 1 == 1?
"1 < 1?"
fib[1] < fib_head_reversed[11]
"1 > 1?"
fib[1] > fib_head_reversed[11]
"1 <= 1?"
fib[1] <= fib_head_reversed[11]
"1 >= 1?"
fib[1] >= fib_head_reversed[11]
```

all
```{r}
all(words_3$col_is_equal)
all(fib) # FALSE <- 0; TRUE <- !0
all(c(TRUE, FALSE, TRUE, TRUE))
```

vector logic
```{r}
x <- c(1,4,7,NA,12,19,15,NA,20)
x_is_NA <- is.na(x)
x_is_NA

x_no_NA <- x[!x_is_NA]
x_no_NA
```

conditional statements

if
```{r}
if(length(fib) > length(x)) {
  "fib is longer than x"
}

if(length(fib) < length(x)) {
  "fib is shorter than x"
}

if(length(fib) == length(x)) {
  "fib is the same length as x"
}
```

if/else
```{r}
if(length(fib) != length(fib_head_reversed)) {
  "fib is not the same length as fib_head_reversed"
} else {
  "fib is the same length as fib_head_reversed"
}
```

else-if
```{r}
if(fib[1] > fib[2]){
  "fib[1] > fib[2]"
} else if(fib[1] < fib[2]){
  "fib[1] < fib[2]"
} else {
  "fib[1] == fib[2]"
}
```

loops
```{r}
for(i in 1:10){
  print(fib_head_reversed[i]*2)
}
```

while
```{r}
k <- length(x)
while(k > 0) {
  print(x[k] - k)
  k <- k-1
}
```

repeat & break
```{r}
i = length(fib)
repeat {
  print(paste("fib[", i, "] == ", fib[i], sep=""));
  if((fib[i] == fib[i - 1]) | (i < 1)){
    print(paste("fib[", (i - 1), "] == fib[", i, "]", sep=""))
    break
  } else {
    i <- (i - 1);
  }
}
```

next
```{r}
for (i in 1:length(fib)){
  if(!fib[i] %% 2) { # skip even numbers
    next
  } else {
    print(c(i, fib[i]))
  }
}
```

